---
title: "p8105_hw1_wb2366"
auther: Wenhan Bao
Date: 2021-09-28
output: github_document
---

```{r library}
library(tidyverse)
```

## Problem1
- Create a data frame comprised of:
  - a random sample of size 10 from a standard Normal distribution
  - a logical vector indicating whether elements of the sample are greater than 0
  - a character vector of length 10
  - a factor vector of length 10, with 3 different factor “levels”

```{r data frame}
example_df = tibble(
  vec_df = rnorm(10),
  vec_logical = vec_df > 0,
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  vec_factor = factor(c("mid", "low", "high", "mid", "low", "mid", "low", "high", "high", "low"))
)
```

**Try to take the mean of each variable in your dataframe. What works and what doesn't?**

```{r mean_df}
mean_vec_df = mean(pull(example_df, vec_df))
mean_vec_logical = mean(pull(example_df, vec_logical))
mean_vec_char = mean(pull(example_df, vec_char))
mean_vec_factor = mean(pull(example_df, vec_factor))
```

Answer: According to the result, the number and logical vector could be taken the mean while the character and factor vector couldn't be taken the mean



