---
title: "p8105_hw1_wb2366"
auther: Wenhan Bao
Date: 2021-09-28
output: github_document
---

```{r library}
library(tidyverse)
```

## Problem1
- Create a data frame comprised of:
  - a random sample of size 10 from a standard Normal distribution
  - a logical vector indicating whether elements of the sample are greater than 0
  - a character vector of length 10
  - a factor vector of length 10, with 3 different factor “levels”

```{r data frame}
example_df = tibble(
  vec_df = rnorm(10),
  vec_logical = vec_df > 0,
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  vec_factor = factor(c("mid", "low", "high", "mid", "low", "mid", "low", "high", "high", "low"))
)
```

**Try to take the mean of each variable in your dataframe. What works and what doesn't?**

```{r mean_df}
mean_vec_df = mean(pull(example_df, vec_df))
mean_vec_logical = mean(pull(example_df, vec_logical))
mean_vec_char = mean(pull(example_df, vec_char))
mean_vec_factor = mean(pull(example_df, vec_factor))
```

**Answer:** According to the result, the number and logical vector could be taken the mean while the character and factor vector couldn't be taken the mean

**Write a code chunk that applies the as.numeric function to the logical, character, and factor variables (please show this chunk but not the output). What happens, and why? Does this help explain what happens when you try to take the mean?**

```{r convert variables}
con_mean_vec_logical = mean(as.numeric(pull(example_df, vec_logical)))
con_mean_vec_char = mean(as.numeric(pull(example_df, vec_char)))
con_mean_vec_factor = mean(as.numeric(pull(example_df, vec_factor)))
```

**Answer:** After converting variables to numeric, the logical vector and factor vector could be taken the mean in that they could be converted to "0","1" or "1", "2", "3" by ranking. However, we still fail to take the mean of the character vector in that character vector couldn't be converted in to numeric which is still N/A.



## Problem2


```{r load dataset}
data("penguins", package = "palmerpenguins")
```

**The data in this dataset, including names / values of important variables**

**Answer:** 
Species is a `r class(pull(penguins, species))` variable, which has species `r levels(pull(penguins, species))`. 

Island is a `r class(pull(penguins, island))` variable, which has `r levels(pull(penguins, island))` islands.

Bill length (mm) is a `r class(pull(penguins, bill_length_mm))` variable. 
The mean of bill length (mm) is `r round(mean(pull(penguins, bill_length_mm), na.rm=TRUE), digits = 2)`.
The median of Bill length (mm) is `r median(pull(penguins, bill_length_mm), na.rm=TRUE)`.
Values for bill length range from `r range(pull(penguins, bill_length_mm), na.rm=TRUE)`.

Bill depth (mm) is a `r class(pull(penguins, bill_depth_mm))` variable. 
The mean of bill depth (mm) is `r round(mean(pull(penguins, bill_depth_mm), na.rm=TRUE), digits = 2)`. 
The median of bill depth(mm) is `r median(pull(penguins, bill_depth_mm), na.rm=TRUE)`. 
Values for bill depth range from `r range(pull(penguins, bill_depth_mm), na.rm=TRUE)`.

Body mass (g) is a `r class(pull(penguins, body_mass_g))` variable. 
The mean of Body mass (g) is `r round(mean(pull(penguins, body_mass_g), na.rm=TRUE), digits = 2)`. The median of Body mass (g) is `r median(pull(penguins, body_mass_g), na.rm=TRUE)`
Values for bill depth range from `r range(pull(penguins, body_mass_g), na.rm=TRUE)` . 

Flipper length (mm) is a `r class(pull(penguins, flipper_length_mm))` variable. 
The mean of flipper length (mm) is `r round(mean(pull(penguins, flipper_length_mm), na.rm=TRUE), digits = 2)`. 
The median of Flipper length (mm) is `r median(pull(penguins, flipper_length_mm), na.rm=TRUE)`
Values for flipper length range from `r range(pull(penguins, flipper_length_mm), na.rm=TRUE)` .

Sex is a `r class(pull(penguins, sex))` variable, which has `r levels(pull(penguins, sex))` categories.

Year is a `r class(pull(penguins, year))` variable. The range for the years variable is from `r range(pull(penguins, year))`.

**The size of the dataset (using nrow and ncol)**

**Answer:** row= `r nrow(penguins)`, col = `r ncol(penguins)`

**The mean flipper length**

**Answer:** mean of flipper length = `r mean(penguins$flipper_length_mm, na.rm=TRUE)`



